Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-11 02_Paper/paper.tex
table 2.

\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Use Case        & Description \\ \midrule
              Use Case 1  & \begin{minipage}[t]{0.25\textwidth}
                            \begin{description}
                                   \item Conveyor speed: Slow
                                   \item Robot position: OK
                            \end{description}
                            \end{minipage}  \\ \hline
              Use Case 2  & \begin{minipage}[t]{0.25\textwidth}
                            \begin{description}
                                   \item Conveyor speed: Slow
                                   \item Robot position: NOK
                            \end{description}
                            \end{minipage}  \\ \hline
              Use Case 3  & \begin{minipage}[t]{0.25\textwidth}
                            \begin{description}
                                   \item Conveyor speed: Fast
                                   \item Robot position: OK
                            \end{description}
                            \end{minipage}  \\ \hline
              Use Case 4  & \begin{minipage}[t]{0.25\textwidth}
                            \begin{description}
                                   \item Conveyor speed: Fast
                                   \item Robot position: NOK
                            \end{description}
                            \end{minipage}  \\ \hline
              Use Case 5  & \begin{minipage}[t]{0.25\textwidth}
                            \begin{description}
                                   \item Conveyor speed: Too Fast
                                   \item Robot position: OK
                            \end{description}
                            \end{minipage}  \\ \hline
              Use Case 6  & \begin{minipage}[t]{0.25\textwidth}
                            \begin{description}
                                   \item Conveyor speed: Too Fast
                                   \item Robot position: NOK
                            \end{description}
                            \end{minipage}  \\ \bottomrule
       \end{tabular}
       \caption{Industry 4.0 demostration cell: Controlled Use-Cases.
       Use-Cases with the value \textit{Robot position: NOK} and \textit{Conveyor speed: Too Fast} will result in NOK pieces.}
       \label{tab:use_cases}
\end{table}

>>>>

\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Use Case        & Description \\ \midrule
              Use Case 1  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Slow \\
                                   Robot position: OK
                            \end{minipage}  \\ \hline
              Use Case 2  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Slow \\
                                   Robot position: NOK
                            \end{minipage}  \\ \hline
              Use Case 3  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Fast \\
                                   Robot position: OK
                            \end{minipage}  \\ \hline
              Use Case 4  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Fast \\
                                   Robot position: NOK
                            \end{minipage}  \\ \hline
              Use Case 5  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Too Fast \\
                                   Robot position: OK
                            \end{minipage}  \\ \hline
              Use Case 6  & \begin{minipage}[t]{0.25\textwidth}
                                   Conveyor speed: Too Fast \\
                                   Robot position: NOK
                            \end{minipage}  \\ \bottomrule
       \end{tabular}
       \caption{Industry 4.0 demostration cell: Controlled Use-Cases.
       Use-Cases with the value \textit{Robot position: NOK} and \textit{Conveyor speed: Too Fast} will result in NOK pieces.}
       \label{tab:use_cases}
\end{table}
